---
title: "Current Projects"
description: |
  A reflection of topics covered in STA 631 - Summer 2023
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Course Objective 1
#### Describe probability as a foundation of statistical modeling, including inference and maximum likelihood estimation

*From Activity 6 - Logistic Regression*

```{r chunk1}
#load library
library(tidyverse)
library(tidymodels)
```

```{r chunk2}
#read in data from URL
resume <- read_csv("https://www.openintro.org/data/csv/resume.csv")
```

```{r chunk3}
#coerce variable of interest to binary
resume$received_callback <- factor(resume$received_callback)
```

```{r chunk4}
# probability of getting a callback
prob_yes = 392/4870
prob_yes

odds_yes = (prob_yes/ (1-prob_yes))
odds_yes
```

**Logistic Regression**
```{r}
resume_mod <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(received_callback ~ race, data = resume, family = "binomial")

tidy(resume_mod) %>% 
  knitr::kable(digits = 3)
```

```{r}
#log odds of perceived black person getting callback
log_odds_callback = -2.68

odds_callback = exp(log_odds_callback)
odds_callback
```

## Discussion & Reflection






---

## Course Objective 2
#### Determine and apply the appropriate generalized linear model for a specific data context

*From Mini Competition 2*








## Discussion & Reflection





---

## Course Objective 3
#### Conduct model selection for a set of candidate models

*From Mini Competition 1*






## Discussion & Reflection



---

## Course Objective 4
#### Communicate the results of statistical models to a general audience

*From Mini Competition 2 - see code above*

## Discussion & Reflection








---

## Course Objective 5
#### Use programming software (i.e., R) to fit and assess statistical models

*See above for examples of R code*

## Discussion & Reflection





