---
title: "Current Projects"
description: |
  A reflection of topics covered in STA 631 - Summer 2023
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Course Objective 1
#### Describe probability as a foundation of statistical modeling, including inference and maximum likelihood estimation

*From Activity 6 - Logistic Regression*

```{r chunk1}
#load library
library(tidyverse)
library(tidymodels)
```

```{r chunk2}
#read in data from URL
resume <- read_csv("https://www.openintro.org/data/csv/resume.csv")
```

```{r chunk3}
#coerce variable of interest to binary
resume$received_callback <- factor(resume$received_callback)
```

```{r chunk4}
# probability of getting a callback
prob_yes = 392/4870
prob_yes

odds_yes = (prob_yes/ (1-prob_yes))
odds_yes
```

**Logistic Regression**
```{r}
resume_mod <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(received_callback ~ race, data = resume, family = "binomial")

tidy(resume_mod) %>% 
  knitr::kable(digits = 3)
```

```{r}
#log odds of perceived black person getting callback
log_odds_callback = -2.68

odds_callback = exp(log_odds_callback)
odds_callback
```

## Discussion & Reflection






---

## Course Objective 2
#### Determine and apply the appropriate generalized linear model for a specific data context

*From Mini Competition 2*

```{r}
library(tidyverse)
raw_data <- read_csv("inventory.csv")
```


#convert week data by month #easier for interpretation
```{r}
data_month <- raw_data %>% mutate(Month = case_when(week <= 4 ~ 'July',
                                                    week > 4 & week <= 8 ~ 'August',
                                                    week > 8 & week <= 12 ~ 'September',
                                                    week > 12 & week <= 16 ~ 'October',
                                                    week > 16 & week <= 20 ~ 'November',
                                                    week > 20 & week <= 24 ~ 'December',
                                                    week > 24 & week <= 28 ~ 'January',
                                                    week > 28 & week <= 32 ~ 'February',
                                                    week > 32 & week <= 37 ~ 'March',
                                                    week > 37 & week <= 41 ~ 'April',
                                                    week > 41 & week <= 45 ~ 'May',
                                                    week > 45 & week <= 50 ~ 'June',
                                                    week > 50 & week <= 53 ~ 'July2',))

data_month$Month <- factor(data_month$Month, levels = c("July", "August", "September",
                                                        "October", "November", "December",
                                                        "January", "February", "March",
                                                        "April", "May", "June", "July2"))
data_month$item_no <- factor(data_month$item_no)
```

#add binary info
```{r}
data_month_bi <- data_month %>% mutate(sold_binary = case_when(sold > 0 ~ '1',
                                                    TRUE ~ '0' ))

data_month_bi$sold_binary <- as.numeric(data_month_bi$sold_binary)
```


```{r}
data_wider <- data_month %>% pivot_wider(names_from = item_no,
                                    values_from = sold)

data_wider
```


#see overall trends across time
```{r}
ggplot(data = data_month, aes(x = Month,
                             y = sold,
                             color = item_no,
                             fill = item_no)) +
  geom_col() + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        legend.position = "none")
```


```{r}
summary(data_month_bi)
```


#Split data

```{r}
#install.packages("caTools")
library(caTools)
set.seed(123)
split_data <- sample.split(data_month_bi$sold, SplitRatio = 0.7)

test_data <- subset(data_month_bi, split_data == FALSE)

train_data <- subset(data_month_bi, split_data == TRUE)
```


#model 1
```{r}
fit <- glm(sold_binary ~ Month + item_no, data=train_data, family=binomial())

summary(fit)
```

```{r}
set.seed(123)
split_data2 <- sample.split(data_month$sold, SplitRatio = 0.7)

test_data2 <- subset(data_month, split_data2 == FALSE)

train_data2 <- subset(data_month, split_data2 == TRUE)

fit2 <- glm(sold ~ Month + item_no, data = train_data2)

summary(fit2)
```


```{r}
library(broom)

model <- tidy(fit)
options(scipen = 999)
model
```

#get variables with p value less than 0.05
```{r}
sig <- subset(model, p.value < 0.05)
print(sig, n = 114)
```


#predictions
```{r}
test_data$prob <- predict(fit, test_data, type="response")

test_data$pred <- test_data %>% mutate(ifelse(prob > .75, "1", "0"))
```

```{r}
accuracy <- mean(head(test_data$pred$`ifelse(prob > 0.75, "1", "0")`, 35) == head(test_data$sold_binary, 35))
accuracy #77% accuracy
```

#predictions for fit2
```{r}
test_data2$prob <- predict(fit2, test_data2, type="response")

test_data2$pred <- test_data2 %>% mutate(ifelse(prob > .75, "1", "0"))
```

```{r}
accuracy2 <- mean(head(test_data2$pred$`ifelse(prob > 0.75, "1", "0")`, 35) == head(test_data2$sold, 35))
```


#what is our second model predicting at?
```{r}
accuracy2 #2% accuracy
```

*Our first model is predicting with 77% accuracy*

## Discussion & Reflection
Mini competition 2 set the goal to create a model to complete the task of projecting a company’s sales of widgets and then communicate our findings to a general audience. In this example, we utilized a generalized linear model approach to accomplish this task and framed the output in terms of months of projected high sales. This way, the company was able to use our predictions to choose which widgets should be kept in excess stock during specific months. One of the main goals of this assignment was to intentionally frame the output and predictions in a manner that is easily digestible to people who are not formally trained in statistics. A challenge of this goal was to strike a balance between effective communication without condescension- this is often a critique which non-academics have with academia. 

One problem with our approach to the generalized linear model was with our training and testing models. While we randomized the dataset and split our data into a 70:30 training and testing sets, this ignores the collinearity of the data. For example, it is possible that one widget over multiple months could have been selected for either the training or testing sets. To ensure an even separation of widgets, a better approach would have been to select by unique widget and then subset the data. 





---

## Course Objective 3
#### Conduct model selection for a set of candidate models

*From Mini Competition 1*






## Discussion & Reflection



---

## Course Objective 4
#### Communicate the results of statistical models to a general audience

*From Mini Competition 2 - see code above*

## Discussion & Reflection








---

## Course Objective 5
#### Use programming software (i.e., R) to fit and assess statistical models

*See above for examples of R code*

## Discussion & Reflection





